r ---
title: "Analysis"
author: "Alicia Canales"
date: "2023-05-04"
output: 
  html_document:
    code_folding: 'hide'
---

```{r setup, include=FALSE, message=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, results=FALSE, message=FALSE)
# removed "include" to plot figues on the Markdown
```

```{r}
library(tidyverse)
library(here)
library(janitor)
library(readxl)
library(tsibble)
library(lubridate)
library(feasts)
library(patchwork)
library(kableExtra)
library(purrr)
library(quadprog)
```

### Importing data **this is only the first page of the excel sheet**
```{r}
coho <- readxl::read_xlsx(here('data', 'OC Coho Abundance.xlsx')) %>%
  clean_names() %>% 
  distinct()
```


### Figures of each population from 1994-2019
```{r}
coho_yr <- coho %>%
  mutate(date = lubridate::mdy(year)) #Convert to date for tibble, this didn't work tho so we need to revisit this.

coho_ts <- coho_yr %>%
 as_tsibble(key = NULL, index = year) #Convert to tibble for timeseries, this didn't work tho so we need to revisit this.

pop_alsea <- ggplot(data = coho_ts, aes(x = year, y = alsea)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Alsea") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_beaver <- ggplot(data = coho_ts, aes(x = year, y = beaver)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Beaver") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_coos <- ggplot(data = coho_ts, aes(x = year, y = coos)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Coos") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_coquille <- ggplot(data = coho_ts, aes(x = year, y = coquille)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Coquille") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_floras <- ggplot(data = coho_ts, aes(x = year, y = floras)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Floras") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_lower_umpqua <- ggplot(data = coho_ts, aes(x = year, y = lower_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Lower Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_middle_umpqua <- ggplot(data = coho_ts, aes(x = year, y = middle_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Middle Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_necanicum <- ggplot(data = coho_ts, aes(x = year, y = necanicum)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Necanicum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_nehalem <- ggplot(data = coho_ts, aes(x = year, y = nehalem)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Mehalem") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_nestucca <- ggplot(data = coho_ts, aes(x = year, y = nestucca)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Nestucca") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_north_umpqua <- ggplot(data = coho_ts, aes(x = year, y = north_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "North Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_salmon <- ggplot(data = coho_ts, aes(x = year, y = salmon)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Salmon") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_siletz <- ggplot(data = coho_ts, aes(x = year, y = siletz)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Siletz") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_siltcoos <- ggplot(data = coho_ts, aes(x = year, y = siltcoos)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Siltcoos") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_siuslaw <- ggplot(data = coho_ts, aes(x = year, y = siuslaw)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Siuslaw") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_sixes <- ggplot(data = coho_ts, aes(x = year, y = sixes)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Sixes") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_south_umpqua <- ggplot(data = coho_ts, aes(x = year, y = south_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "South Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_tahkenitch <- ggplot(data = coho_ts, aes(x = year, y = tahkenitch)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Tahkenitch") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_tenmile <- ggplot(data = coho_ts, aes(x = year, y = tenmile)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Tenmile") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_tillamook <- ggplot(data = coho_ts, aes(x = year, y = tillamook)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Tillamook") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

pop_yaquina <- ggplot(data = coho_ts, aes(x = year, y = yaquina)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Population Count",
      title = "Yaquina") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))


#pop_alsea
#pop_beaver
#pop_coos
#pop_coquille
#pop_floras
#pop_lower_umpqua
#pop_middle_umpqua
#pop_necanicum
#pop_nehalem
#pop_nestucca
#pop_north_umpqua
#pop_salmon
#pop_siletz
#pop_siltcoos
#pop_siuslaw
#pop_sixes
#pop_south_umpqua
#pop_tahkenitch
#pop_tenmile
#pop_tillamook
#pop_yaquina
```

### Panel of figures of Y(it) - Annual population for each independent population
```{r}
patchwork::plot_layout(pop_alsea + pop_beaver + pop_coos + pop_coquille)

patchwork::plot_layout(pop_floras + pop_lower_umpqua + pop_middle_umpqua + pop_necanicum)

patchwork::plot_layout(pop_nehalem + pop_nestucca + pop_north_umpqua + pop_salmon)

patchwork::plot_layout(pop_siletz + pop_siltcoos + pop_siuslaw + pop_sixes)

patchwork::plot_layout(pop_south_umpqua + pop_tahkenitch + pop_tenmile + pop_tillamook)

patchwork::plot_layout(pop_yaquina)
```


### Population Mean, Population Variance, and Population SD
```{r}
pop_mean <- sapply(coho[2:22], mean)
pop_variance <- sapply(coho[2:22], var)
pop_sd <- sapply(coho[2:22], sd)

population_df <- data.frame(pop_mean, pop_variance, pop_sd) #combine data into one data frame

## Plot table
population_table <- population_df %>% 
  kable(col.names = c("Population Mean", "Population Variance", "Pop SD")) %>% 
  kable_styling(bootstrap_options = "striped",
                position = "left", full_width = FALSE)

population_table

## In case we need to get the variance of a population (instead of a sample):
# var_pop <- function(x) {
#   mean((x-mean(x))^2)
# }

# var_pop(coho$alsea)
```


### Covariance of each population
```{r, results = TRUE}
## Calculate covariance
population_cov <- cov(coho[2:22])

# population_cov

## Only show bottom triangle of covariances
upper<-population_cov
upper[upper.tri(population_cov)] <-""
upper<-as.data.frame(upper)
upper

```


### Returns of each population
```{r}
## running a for loop to pass this function to each population in the dataset
calculate_returns <- function(data) {
  rt <- numeric(length(data) - 1)  
  for (i in 2:length(data)) {
    rt[i-1] <- (data[i-1] / data[i]) - 1
  }
  return(rt)
} ## i-1 is the current population for whatever year we are looking at and i is the initial population from the previous year

returns <- data.frame(apply(coho[2:22], 2, calculate_returns))

```


### Returns mean, returns sd, returns variance
```{r}
## calculation for returns

## means of the returns for each population
pop_return_mean <- sapply(returns, mean)

## mean of ALL means -- should return one number: 0.774
mean_returns <- mean(pop_return_mean)


## variance of the returns
pop_return_variance <- sapply(returns, var)

## mean of ALL variances -- should return one number: 6.889
mean_variance <- mean(pop_return_variance)

pop_return_sd <- sapply(returns, sd)


## putting everything into a data frame and nice table
return_df <- data.frame(pop_return_mean, pop_return_variance, pop_return_sd)

return_table <- return_df %>% 
  kable(col.names = c("Returns Mean", "Returns Variance", "Returns SD")) %>% 
  kable_styling(bootstrap_options = "striped",
                position = "left", full_width = FALSE)


return_table
```

### Covariance of returns -- (Dmat)
```{r, results = TRUE}

## Calculate variance covariance matrix. 
dmat <- cov(returns) #This is the variance covariance matrix which is amat (diagonal is the variance) that will be inputted into Quadprog

# pop_cov

## Only show bottom triangle of covariances
upper<-dmat
upper[upper.tri(dmat)] <-""
upper<-as.data.frame(upper)
upper

dmat
```

### Plotting R(it) -- Returns
```{r}

# combining date column to new returns df
returns_yr<- cbind(returns, coho_yr$year[-1]) %>% 
  rename('year' = 'coho_yr$year[-1]')

return_ts <- returns_yr %>%
 as_tsibble(key = NULL, index = year)

rt_alsea <- ggplot(data = return_ts, aes(x = year, y = alsea)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Alsea") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_beaver <- ggplot(data = return_ts, aes(x = year, y = beaver)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Beaver") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_coos <- ggplot(data = return_ts, aes(x = year, y = coos)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Coos") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_coquille <- ggplot(data = return_ts, aes(x = year, y = coquille)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Coquille") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_floras <- ggplot(data = return_ts, aes(x = year, y = floras)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Floras") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_lower_umpqua <- ggplot(data = return_ts, aes(x = year, y = lower_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Lower Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_middle_umpqua <- ggplot(data = return_ts, aes(x = year, y = middle_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Middle Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_necanicum <- ggplot(data = return_ts, aes(x = year, y = necanicum)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Necanicum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_nehalem <- ggplot(data = return_ts, aes(x = year, y = nehalem)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Mehalem") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_nestucca <- ggplot(data = return_ts, aes(x = year, y = nestucca)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Nestucca") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_north_umpqua <- ggplot(data = return_ts, aes(x = year, y = north_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "North Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_salmon <- ggplot(data = return_ts, aes(x = year, y = salmon)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Salmon") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_siletz <- ggplot(data = return_ts, aes(x = year, y = siletz)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Siletz") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_siltcoos <- ggplot(data = return_ts, aes(x = year, y = siltcoos)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Siltcoos") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_siuslaw <- ggplot(data = return_ts, aes(x = year, y = siuslaw)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Siuslaw") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_sixes <- ggplot(data = return_ts, aes(x = year, y = sixes)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Sixes") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_south_umpqua <- ggplot(data = return_ts, aes(x = year, y = south_umpqua)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "South Umpqua") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_tahkenitch <- ggplot(data = return_ts, aes(x = year, y = tahkenitch)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Tahkenitch") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_tenmile <- ggplot(data = return_ts, aes(x = year, y = tenmile)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Tenmile") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_tillamook <- ggplot(data = return_ts, aes(x = year, y = tillamook)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Tillamook") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

rt_yaquina <- ggplot(data = return_ts, aes(x = year, y = yaquina)) +
  geom_line(color = "#453781FF") +
  scale_x_continuous(breaks=seq(1994, 2019, by = 1)) +
  labs(x = "Year",
      y = "Return",
      title = "Yaquina") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```



### Panel of figures of R(it) - Annual returns for each independent population
```{r}
patchwork::plot_layout(rt_alsea + rt_beaver + rt_coos + rt_coquille)

patchwork::plot_layout(rt_floras + rt_lower_umpqua + rt_middle_umpqua + rt_necanicum)

patchwork::plot_layout(rt_nehalem + rt_nestucca + rt_north_umpqua + rt_salmon)

patchwork::plot_layout(rt_siletz + rt_siltcoos + rt_siuslaw + rt_sixes)

patchwork::plot_layout(rt_south_umpqua + rt_tahkenitch + rt_tenmile + rt_tillamook)

patchwork::plot_layout(rt_yaquina)
```


### Developing amat, bvec, dmat, and dvec
```{r}

## first row of amat
mean_returns_df <- data.frame(0.5195554, 0.8668412, 1.0668467, 0.8037888, 0.8741770, 0.6100251, 0.6810882, 0.4573553, 0.4978172, 0.8339032, 0.0761665, 2.5722876, 0.5931486, 0.2879635, 0.6849828, 0.9460155, 0.7222910, 0.7872894, 0.3794362, 1.0945078, 0.9048277) # making  df with just the mean returns from each population
colnames(mean_returns_df) <- c('1':'21') # renaming column headers

## second row of amat
line_2_df <- data.frame(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1) #Create a row of 1's
colnames(line_2_df) <- c('1':'21') #Rename column headers

## bottom of amat
id_matrix <- diag(21) #Create identity matrix 21x21
colnames(id_matrix) <- c('1':'21')

amat<- rbind(mean_returns_df, line_2_df, id_matrix)

## bvec with our mean of all pop returns 
bvec <- data.frame(mean_returns,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0) 
colnames(bvec) <- c('1':'23') #Rename column headers

## dmat
dmat <- cov(returns)

dmat_new <- dmat
dmat_new[12,12]=10


## making everything as a matrix for quadprog
amat_matrix <- t(as.matrix(amat)) #Create amat data frame 

bvec_matrix <- t(as.matrix(bvec))

dvec_matrix <- t(as.matrix(rep(0,21)))
```

### Running quadprog
```{r}
y <- solve.QP(dmat, dvec_matrix, amat_matrix, bvec_matrix, meq = 2)
y

sum(y$solution) #1 var_star = .549
r_list <- c(r_max = max(y$solution), 
            r_min = min(y$solution)) #high returns low variance for largest
 ## so this min is a negative number so I should make it .0001 right?

##Clean up code and run it as a loop to try to create graph
##Change bvec with new Rbar
##Table of all Rbar and corresponding $values and plot

```

### Mapping 
```{r}
## i made r_max then highest returns and r_min the lowest of terms. I think this is what nathan said to do. 

bvec_max_matrix <- bvec 

bvec_max_matrix[1,1] = r_max
y <- solve.QP(dmat, dvec_matrix, amat_matrix, bvec_max_matrix, meq = 2)
y ## $value = 0.13559

## made a function for solve.QP
mpt_fun <- function(r, dmat, dvec_matrix, amat_matrix, bvec_matrix) {
  y = solve.QP(dmat, dvec_matrix, amat_matrix, bvec_max_matrix, meq = 2)
  return(y)
}

## i thought this is something we could do.. it doesnt run because the error reads that the length of the list i want to feed into the function is too long?
df <- map(.x = r_list , .f= mpt_fun(r_list, dmat, dvec_matrix, amat_matrix, bvec_matrix))

```














